The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-05-01 paper.qmd
adjusted pixelmap code

# set Base colours
basecols <- brewer.pal(8, name = "YlOrRd")
# recurvisely decrease value
v_val = 0.5
bivariatepal <- c(basecols,
                  colsupress(basecols, sat=v_val),
                  colsupress(colsupress(basecols, sat=v_val), sat=v_val),
                  colsupress(colsupress(colsupress(basecols, sat=v_val), sat=v_val), sat=v_val))
# establish levels of palette
names(bivariatepal) <- paste(rep(1:8, 4), "-" , rep(1:4, each=8), sep="")
# preview palette
#show_col(bivariatepal, ncol=8)

@@

names(VSUP) <- paste(rep(1:8, 4), "-" , rep(1:4, each=8), sep="")
#show_col(VSUP, ncol=8)

@@

mypixelmap <- function(obj){

  if(class(obj)[1] != "pixelmap")
    stop("Object is not of class 'pixelmap'.")

  p <- ggplot()  +
    geom_polygon(
      data = obj$output_data,
      aes_string(
        x = 'long',
        y = 'lat',
        fill = 'values',
        colour = 'values',
        group = 'group'
      )
    )  +
    scale_fill_distiller(
      type = "seq", 
      palette = "YlOrRd", 
      direction = 1,
      name = obj$key_label,
      limits = obj$limits) +

    scale_colour_distiller(
      type = "seq", 
      palette = "YlOrRd", 
      direction = 1,
      limits = obj$limits
    ) +
    guides(colour = "none")  +
    geom_path(
      data = obj$bord,
      aes_string(x = 'long', y = 'lat', group = 'group'),
      colour = "black"
    )  +
    coord_fixed(xlim = c(obj$bbox[1], obj$bbox[3]),
                    ylim = c(obj$bbox[2], obj$bbox[4])) +
    theme(
      axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.background = element_blank()
    )

  p

}

p4a <- mypixelmap(pmap_a) + theme(legend.position="none")

@@

p4b <- mypixelmap(pmap_b) + theme(legend.position="none")

>>>>

# set Base colours
basecols <- brewer.pal(8, name = "YlOrRd")
# recurvisely decrease value
v_val = 0.5
bivariatepal <- c(basecols,
                  colsupress(basecols, sat=v_val),
                  colsupress(colsupress(basecols, sat=v_val), sat=v_val),
                  colsupress(colsupress(colsupress(basecols, sat=v_val), sat=v_val), sat=v_val))
# establish levels of palette
names(bivariatepal) <- paste(rep(1:8, 4), "-" , rep(1:4, each=8), sep="")
# preview palette
show_col(bivariatepal, ncol=8)

@@

names(VSUP) <- paste(rep(1:8, 4), "-" , rep(1:4, each=8), sep="")
show_col(VSUP, ncol=8)

@@

p4b <- view(pmap_a) +
    scale_fill_distiller(
      type = "seq", 
      palette = "YlOrRd", 
      direction = 1) +
  scale_colour_distiller(
      type = "seq", 
      palette = "YlOrRd", 
      direction = 1) +
  theme(legend.position="none")

@@

p4b <- view(pmap_b) +
    scale_fill_distiller(
      type = "seq", 
      palette = "YlOrRd", 
      direction = 1) +
  scale_colour_distiller(
      type = "seq", 
      palette = "YlOrRd", 
      direction = 1) +
  theme(legend.position="none")
